Add Plant Functional Type (PFT) labels

### 2021-04-05 R/add_plant_functional_type.Rmd
keeping height values with each spectrum. need to figure out how to simplify the growthForm values, just keep last word of each

>>>>

## Use NEON growthForm observations

```{r}
library(neonUtilities)
```

```{r}
# download woody vegetation structure data for all sites and years 
out_dir <- here::here("analysis","data","raw_data")

neonUtilities::zipsByProduct(dpID = "DP1.10098.001",
              savepath = out_dir,
              check.size = FALSE)

stackByTable(file.path(out_dir, "filesToStack10098"), folder = TRUE)
```

```{r}
# read the vst_apparentindividual table, which has growthForm data
vst_apparentindividual <- read_csv(out_dir <- here::here("analysis","data","raw_data", "filesToStack10098",
                                                         "stackedFiles", "vst_apparentindividual.csv"))

# select the growthForm and height columns
growthForms <- vst_apparentindividual %>% 
  select(individualID, growthForm, height)

# join the growthForm and height columns into the spectra data frame
cleaned_spectra_merged <- right_join(cleaned_spectra, growthForms, by = "individualID")

# print all unique growthForm values 
unique(cleaned_spectra_merged$growthForm)

# simplify the growth form into "tree" or "shrub" 
cleaned_spectra_merged <- cleaned_spectra_merged %>%

```{r}
# summarize the merged growthform data
cleaned_spectra_merged %>% 
  distinct(spectraID, .keep_all = TRUE) %>% 
  group_by(genusSpecies, growthForm) %>% 
    tally() 
```
